Reanalysis Step 7: Missingness Pattern Analysis

### 2025-09-01 reanalysis-7-missingness_patterns.qmd
fix ai idiiocy

# Arrange plots
if (length(plots) > 0) {
  do.call(grid.arrange, c(plots, ncol = 2))
}
```

>>>>

# Arrange plots
if (length(plots) > 0) {
  # Remove NULL elements from plots list
  plots <- plots[!sapply(plots, is.null)]

  if (length(plots) == 1) {
    print(plots[[1]])
  } else if (length(plots) > 1) {
    do.call(grid.arrange, c(plots, list(ncol = 2)))
  }
}
```
